### 2017-03-01 paper/chapters/sigmoid_belief_nets.tex
add todo for SBN
fixed captions (short caption)
describe the sigmoid func and weights using 'conditions'

\section{Sigmoid Belief Networks}
\label{sec:sbn}
\begin{figure}[htb]
\centering
\input{media/sbn_architecture}
  \caption{Conceptual architecture of belief nets}
  \label{fig:sbn_arch}
  \medskip
  \small
  Bayesian networks, also called belief nets are an acyclic directed graph where blue nodes indicate hidden variables and red nodes represent observed variables.
  Arrows indicate stochastic dependency.
  Even though most belief nets are divided into many layers in the context of deep learning, the original definition does not specify that and thus indicates the dashed arrow the possibility of inter-layer dependencies.
\end{figure}

Sigmoid Belief Networks (SBN) were proposed in 1992 by R.M. Neal \cite{neal:1992} representing a specific type of bayesian networks \cite{pearl:1985} shown in figure \ref{fig:sbn_arch}
In the case of SBNs however, all states are binary and the activation function is the sigmoid function. They are one of the earliest neural networks used for generative modeling, predating all other presented models in this article.
%As described in the overview above, SBNs contain a number of binary states $s$, most commonly divided into many layers.
Each state $s_i$ is a random variable in the bayesian framework which means it can be observed, hidden or unknown representing different states of knowledge. As such it can also be interpreted with a probability distribution.
\begin{equation}
  \label{eq:sbn_node}
p(s_i) = \sigma\bigg(\sum_{j<i}W_{i,j}s_j+b_i\bigg)
\end{equation}
In Equation \ref{eq:sbn_node}, $\sigma$ denotes the sigmoid function $\frac{1}{1 + e^{-x}}$ and $W_{i,j}$ the connection weights from state $s_j$ to $s_i$.

To draw samples from this network, it is possible to simply evaluate Equation \ref{eq:sbn_node} for each visible node.
However prior to that, the SBN first needs to learn how to generate good samples which includes the \emph{learning} and the \emph{inference} problem.\\
Learning means in this context to adjust the weights and biases of the network to be more likely to generate previously observed input.
Meanwhile statistical inference is tasked to infer the states of the hidden nodes based on the states in the visible layer.\\

@@

>>>>

\section{Sigmoid Belief Networks}
\label{sec:sbn}
\begin{figure}[htb]
\centering
\input{media/sbn_architecture}
  \caption[Architecture of Sigmoid Belief Nets]{Conceptual architecture of belief nets}
  \label{fig:sbn_arch}
  \medskip
  \small
  Bayesian networks, also called belief nets are an acyclic directed graph where blue nodes indicate hidden variables and red nodes represent observed variables.
  Arrows indicate stochastic dependency.
  Even though most belief nets are divided into many layers in the context of deep learning, the original definition does not specify that and thus indicates the dashed arrow the possibility of inter-layer dependencies.
\end{figure}

Sigmoid Belief Networks (SBN) were proposed in 1992 by R.M. Neal \cite{neal:1992} representing a specific type of bayesian networks \cite{pearl:1985} shown in figure \ref{fig:sbn_arch}
In the case of SBNs however, all states are binary and the activation function is the sigmoid function. They are one of the earliest neural networks used for generative modeling, predating all other presented models in this article.
%As described in the overview above, SBNs contain a number of binary states $s$, most commonly divided into many layers.
Each state $s_i$ is a random variable in the bayesian framework which means it can be observed, hidden or unknown representing different states of knowledge. As such it can also be interpreted with a probability distribution.
\begin{equation}
  \label{eq:sbn_node}
p(s_i) = \sigma\bigg(\sum_{j<i}W_{i,j}s_j+b_i\bigg)
\end{equation}
where 
\begin{conditions}
  \sigma(x) & $\frac{1}{1 + e^{-x}}$ (sigmoid function)\\
  W_{i,j} & connection weights from state $s_i$ to $s_j$\\
\end{conditions}

To draw samples from this network, it is possible to simply evaluate Equation~\ref{eq:sbn_node} for each visible node.
However prior to that, the SBN first needs to learn how to generate good samples which includes the \emph{learning} and the \emph{inference} problem.\\
Learning means in this context to adjust the weights and biases of the network to be more likely to generate previously observed input.
Meanwhile statistical inference is tasked to infer the states of the hidden nodes based on the states in the visible layer.\\

@@

% TODO: connection to DBN, layer-wise greedy training
% Hinton et al. (2006)
